---
title: "STM"
author: "Jilung Hsieh"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    highlight: zenburn
    fig_width: 8
    fig_height: 4
    fig_caption: yes
    df_print: tibble
    params:
        output_dir:"html"
---

# STM Tutorials

-   <https://juliasilge.com/blog/sherlock-holmes-stm/>
-   [RPubs - stm_course](https://rpubs.com/Rawrion/669023)

# Setups

```{r loading-pkgs}
pkgs <- c("LDAvis", "tidyverse", "jiebaR", "igraph", "stm", "wordcloud")
install.packages(pkgs[!pkgs %in% installed.packages()]) 
library(tidyverse)
library(tidyr) 
options(scipen = 999)
```

```{r}
load("data/s3_watched.rda")
Sys.setlocale(locale="zh_TW.UTF-8")

```

```{r initial-jieba}
library(jiebaR)
stopWords <- readRDS("data/stopWords.rds")
segment_not <- c("爸爸", "爸媽", "新手")
watched <- c("爸爸","父親","老公","先生","丈夫","奶爸","寶爸","隊友",
             "爹地","爸比","把拔","把鼻","老爸","另一半","拔拔",
             "孩子的爸","孩子爸", "爸拔","他爸","她爸","新手爸","版爸",
             "板爸","我家男人","當爸的","腦公","阿爸","人父","孩子的爹",
             "孩子爹","老爹","外子","拔比","爸鼻","爸把","爸逼","爸咪",
             "把爸","拔爸","爹低","帥爸","準爸","小孩爸","親爸","神爸",
             "宅爸","瓶餵爸","寶寶的爸","孩的爸","女兒的爸")

reserved <- c("神隊友", "豬隊友", "好隊友", "好先生", "好爸爸", "好老公")

watched <- c(watched, reserved)

watched.str <- paste0(watched, collapse = "|")


reserved <- c("神隊友", "豬隊友", "好隊友", "好先生", "好爸爸", "好老公")

cutter <- worker()
tagger <- worker("tag")
new_user_word(cutter, segment_not)
new_user_word(cutter, watched)
new_user_word(tagger, segment_not)
new_user_word(tagger, watched)
```

# Pre-processing

## Tokenization

```{r}
unnested.df <- s3.watched %>%
    # filter(str_detect(sentence, "隊友")) %>%
    mutate(word = purrr::map(s3, function(x)segment(x, cutter))) %>%
    unnest(word) %>%
    anti_join(stopWords) %>%
    filter(!str_detect(word, "[a-zA-Z0-9]+")) %>%
    filter(!is.na(word)) %>%
    group_by(word) %>%
    filter(n() > 5) %>%
    ungroup() %>%
    filter(nchar(word) > 1)
```

## Building dfm

```{r dfm}
library(tidytext)
# library(quanteda)
dfm <- unnested.df %>%
    count(doc_id, word, sort = TRUE) %>%
    cast_dfm(doc_id, word, n) #tidytext
```

# STM

```{r stm}
library(stm)
topic_model <- stm(dfm, K = 12, verbose = F)
save(topic_model, file="output/tm02_s3_k12.rda")
load("output/tm02_s3_k12.rda")
```

```{r summary-of}
summary(topic_model)
# print(topic_model)
```

```{r topic-corr}
library(igraph)
mod.out.corr <- topicCorr(topic_model)
# install.packages("wordcloud")

cloud(topic_model, topic = 7, scale = c(4,.5), family = "Heiti TC Light")

plot(mod.out.corr)
mod.out.corr
```

## LDAvis

See Sievert, C., & Shirley, K. (2014). LDAvis: A method for visualizing and interpreting topics. *Proceedings of the Workshop on Interactive Language Learning, Visualization, and Interfaces*. Proceedings of the Workshop on Interactive Language Learning, Visualization, and Interfaces, Baltimore, Maryland, USA. <https://doi.org/10.3115/v1/w14-3110>

1.  saliency(term w) = frequency(w) \* [sum_t p(t \| w) \* log(p(t \| w)/p(t))] for topics t; see Chuang et. al (2012)

<!-- -->

2.  relevance(term w \| topic t) = λ \* p(w \| t) + (1 - λ) \* p(w \| t)/p(w); see Sievert & Shirley (2014). Lift: p(w\|t)/p(w) = p(w and t)/(p(w)p(t))

```{r toLDAvis}
stm.doc <- quanteda::convert(dfm, to = "stm")
toLDAvis(topic_model, stm.doc$documents)
```

```{r}
# topics <- c("隊友", "生產經驗", "Mothering", "大寶",
#             "先生", "夫妻之間", "神隊友", "好隊友", "豬隊友", 
#             "育兒溝通", "婆婆", "爸爸")
labelTopics(topic_model)
??labelTopics 
findThoughts(topic_model)
??findThoughts
```
